Measuring contrast processing in the visual system using the steady state visually evoked potential (SSVEP)

### 2024-12-01 review.qmd
Changing figure numbers
Fixed new figure rendering

![Illustration of a sinusoidal input signal (left), its Fourier spectrum (middle), and how the amplitude of the first harmonic component increases with contrast (right). These calculations assume an entirely linear system.](){#fig-fullwaverectification}
:::
::: {.content-visible unless-format="docx"}
![Illustration of a full-wave rectified sinusoid (left), its Fourier spectrum (middle), and how the amplitude of the first harmonic component increases with contrast (right).](Figures/3_fullwaverectification.pdf){#fig-fullwaverectification}
:::

@@

![Illustration of how a sinusoidal input signal is affected by a nonlinear transducer. The input wavefore (left panel) is frequency doubled by the squaring operator, and now features energy at the second harmonic (10Hz) and its multiple (middle panel). The contrast response function at the second harmonic is now nonlinear, and saturates at high contrasts (right panel).](){#fig-transducer}
:::
::: {.content-visible unless-format="docx"}
![Illustration of how a sinusoidal input signal is affected by a nonlinear transducer. The input wavefore (left panel) is frequency doubled by the squaring operator, and now features energy at the second harmonic (10Hz) and its multiple (middle panel). The contrast response function at the second harmonic is now nonlinear, and saturates at high contrasts (right panel).](Figures/4_transducer.pdf_transducer.pdf){#fig-transducer}
:::

@@

![Demonstration of how two inputs of different frequencies are processed by a nonlinear transducer. Additional harmonics are apparent in the Fourier spectrum (middle panel), and the contrast response function is suppressed (right panel). The effects of using different nonlinearities can be explored in the accompanying code.](){#fig-twoinputs}
:::
::: {.content-visible unless-format="docx"}
![Demonstration of how two inputs of different frequencies are processed by a nonlinear transducer. Additional harmonics are apparent in the Fourier spectrum (middle panel), and the contrast response function is suppressed (right panel). The effects of using different nonlinearities can be explored in the accompanying code.](Figures/4_twoinputs.pdf){#fig-twoinputs}
:::

@@

![Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts. The solid line is the linear regression fit to the lowest four data points prior to the satuating part of the curve, and the dashed line extrapolates the fit back to determine the contrast value when y=0, which gives a threshold estimate (red point).](){#fig-sweepvep}
:::
::: {.content-visible unless-format="docx"}
![Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts. The solid line is the linear regression fit to the  lowest four data points prior to the satuating part of the curve, and the dashed line extrapolates the fit back to determine the contrast value when y=0, which gives a threshold estimate (red point).](Figures/5_sweepplot.pdf){#fig-sweepvep}
:::

@@

::: {.content-visible unless-format="docx"}
![Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) from Afsari et al. (2014). One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity (red) compared to control animals (black).](Figures/6_clinicalplot.pdf){#fig-plotclinical}
:::

>>>>

::: {.content-visible when-format="docx"}
- FIGURE ABOUT HERE
![Illustration of a sinusoidal input signal (left), its Fourier spectrum (middle), and how the amplitude of the first harmonic component increases with contrast (right). These calculations assume an entirely linear system.](){#fig-fullwaverectification}
:::
::: {.content-visible unless-format="docx"}
![Illustration of a full-wave rectified sinusoid (left), its Fourier spectrum (middle), and how the amplitude of the first harmonic component increases with contrast (right).](Figures/3_fullwaverectification.pdf){#fig-fullwaverectification}

:::

@@

![Illustration of how a sinusoidal input signal is affected by a nonlinear transducer. The input wavefore (left panel) is frequency doubled by the squaring operator, and now features energy at the second harmonic (10Hz) and its multiple (middle panel). The contrast response function at the second harmonic is now nonlinear, and saturates at high contrasts (right panel).](){#fig-transducer}
:::
::: {.content-visible unless-format="docx"}
![Illustration of how a sinusoidal input signal is affected by a nonlinear transducer. The input wavefore (left panel) is frequency doubled by the squaring operator, and now features energy at the second harmonic (10Hz) and its multiple (middle panel). The contrast response function at the second harmonic is now nonlinear, and saturates at high contrasts (right panel).](Figures/4_transducer.pdf){#fig-transducer}
:::

@@

![Demonstration of how two inputs of different frequencies are processed by a nonlinear transducer. Additional harmonics are apparent in the Fourier spectrum (middle panel), and the contrast response function is suppressed (right panel). The effects of using different nonlinearities can be explored in the accompanying code.](){#fig-twoinputs}
:::
::: {.content-visible unless-format="docx"}
![Demonstration of how two inputs of different frequencies are processed by a nonlinear transducer. Additional harmonics are apparent in the Fourier spectrum (middle panel), and the contrast response function is suppressed (right panel). The effects of using different nonlinearities can be explored in the accompanying code.](Figures/5_twoinputs.pdf){#fig-twoinputs}
:::

@@

![Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts. The solid line is the linear regression fit to the lowest four data points prior to the satuating part of the curve, and the dashed line extrapolates the fit back to determine the contrast value when y=0, which gives a threshold estimate (red point).](){#fig-sweepvep}
:::
::: {.content-visible unless-format="docx"}
![Sweep VEP simulation showing how a contrast detection threshold can be estimated from sweep VEP data measured at higher contrasts. The solid line is the linear regression fit to the  lowest four data points prior to the satuating part of the curve, and the dashed line extrapolates the fit back to determine the contrast value when y=0, which gives a threshold estimate (red point).](Figures/6_sweepplot.pdf){#fig-sweepvep}
:::

@@

::: {.content-visible unless-format="docx"}
![Example contrast response functions for different clinical conditions. Panel (a) shows modelled contrast response functions for epilepsy patients (blue) and control participants (black), based on the data of Tsai et al. (2011). Panel (b) shows functions for the amblyopic (red) and fellow (black) eyes of adults with amblyopia, based on the data of Baker et al. (2015). Panel (c) shows functions for children with (green) and without (black) a diagnosis of autism, based on the data of Vilidaite et al. (2018). Panel (d) shows data from *Drosophila melanogaster* (fruit flies) from Afsari et al. (2014). One day-old flies expressing a human gene linked to Parkinson's (hLRRK-G2019S) show increased SSVEP response amplitude and sensitivity (red) compared to control animals (black).](Figures/7_clinicalplot.pdf){#fig-plotclinical}
:::
